---
title: "Week 3 Transformations"
author: "Crystal Quezada"
date: "2024-09-10"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(stringr)
```

#3

(.)\1\1 - Should this read "(.)\\1\\" ? This would repeat a character three times.

"(.)(.)\\2\\1" - This would repeat two characters twice and then reverse.

(..)\1 - This would repeat two characters twice.

"(.).\\1.\\ 1 " - This would repeat two characters three times.

"(.)(.)(.).*\\3\\2\\1" - This would call three characters and then reverse it.

________________________________

#4

Start and end with the same character
```{r same letters}
words <- c("racecar", "america", "radar")
find <- str_detect(words, "^(.).*\\1$")
find
```

Contain a repeated pair of letters (e.g. "church" contains "ch" repeated twice.)
```{r repeated letters}
repeats <- c("church", "coco", "perpendicular")
search <- str_detect(repeats, "(..).*\\1")
search
```

Contain one letter repeated in at least three places (e.g. "eleven" contains three "e"s.)
```{r three}
three <- c("mirror", "terror", "rearrange")
lookup <- str_detect(three, "(.)(^\\1)*\\1(^\\1)*\\1")
lookup
```




